Interactive Tools for Science Advice

### 2019-11-01 analysis/presentation/interactive_tools.Rmd
Draft seminar slides up to the objectives

```{r data}
## xaringan::inf_mr()
library(NCAM)
library(plotly)
load("data/NCAM_2018.RData")
fit <- ncam_2018
tabs <- tidy_model(fit)
ages <- fit$tmb.data$ages
years <- fit$tmb.data$years
years_plus1 <- fit$tmb.data$years_plus1
```

@@

- Discovery is one of the most exciting parts of science
- Visulizations are one of the tools we use to reveal patterns
- Models allow us to simplify and describe these patterns
- At various stages, we need to communicate our findings

>>>>

```{r data}
## xaringan::inf_mr()

library(NCAM)
library(plotly)
library(ggplot2)
library(emojifont)

htmltools::tagList(rmarkdown::html_dependency_font_awesome())

load("data/NCAM_2018.RData")
fit <- ncam_2018
tabs <- tidy_model(fit)
ages <- fit$tmb.data$ages
years <- fit$tmb.data$years
years_plus1 <- fit$tmb.data$years_plus1
```

@@

- Discovery is one of the most exciting parts of science
- Visualizations are one of the tools we use to reveal patterns
- Models allow us to simplify and describe these patterns
- At various stages, we need to communicate our findings

## Communicating information

Simplified workflow:

<hr>

<div style="float: left; width: 20%; text-align: center;">
Data  
<font size="20"><i class="fa fa-database"></i></font>
</div>

<div style="float: left; width: 20%; text-align: center;">
<br>
$\rightarrow$
</div>

<div style="float: left; width: 20%; text-align: center;">
Models  
<font size="20"><i class="fa fa-chart-area"></i></font>
</div>

<div style="float: left; width: 20%; text-align: center;">
<br>
$\rightarrow$
</div>

<div style="float: left; width: 20%; text-align: center;">
Discuss  
<font size="20"><i class="fa fa-comments"></i></font>
</div>

<hr>

<div>
- Connections may not come easy
    - Growing volume and variety of data
    - Increasingly complex models
    - Diverse backgrounds

</div>

## Stock assessments <i class="fa fa-fish"></i>

<div style="float: left; width: 65%;">

- Communicating stock assessment results isn't getting easier  
    - Growing volume and variate of data  
    - Increasingly complex models  
    - Diverse backgrounds  
- Traditional formats sometimes 
    - Overwhelm participants with endless tables and figures
    - Fail to convey the richness of information available

</div>

<div style="float: right; width: 35%;">

```{r, out.width = "100%"}
knitr::include_graphics("figures/doc_screenshots.PNG")
```

</div>

## Interactive tools

<div style="float: left; width: 55%;">

- Simplify communication and improve accessibility
- Common tools that are used daily on a range of websites
- Their use is no longer restricted to website developers
    - Integrated into software commonly used by the research community
    - Surprisingly easy to generate interactive dashboards
    - Growing number of users

</div>

<div style="float: right; width: 40%; padding-left: 5%">

```{r, out.width = "100%"}
knitr::include_graphics("figures/canada_poll_tracker.PNG")
```

</div>

## Objective

- Here we aim to demonstrate that interactive tools simplify our workflow, from data and model exploration to communication
